The application takes \textsc{h.264} formatted video files as
input and outputs them to \textsc{ntsc-dvd} formatted files by making
use of an IaaS provider. End-users upload their \textsc{h.264}
formatted file to a front-end server--which is running our
application--which in its turn makes a job for this file and sends it
to a VM at the IaaS-provider based on the chosen
allocation-policy. Because one job can fully utilize a VM considering
its \textsc{CPU} intensive nature, the allocation-policy considers a
VM free for taking only if it has no current job being run on it. New
VMs will be spawned if the provisioner considers there to be a
shortage of free VMs.

\paragraph{Requirements}
To make the proposed system a successor to the current system, our
solution should adhere to the following requirements to be able to
scale well for future workloads.

\begin{enumerate}[i]
\item The system should be automated for (1) the creation and
  provisioning of the VMs (see also \ref{req:elastic})) and (2)
  the allocation of jobs to VMs.
\item \label{req:elastic} It should support elastic policies to
  scale for sudden demand without human intervention.
\item Statistics are kept so that we can analyze the system for the
  experiments and make better implementation choices for future work.
\item The system should have the means to restart when an error occurs
  which is in our control e.g. a sudden shutdown of our server part.
\end{enumerate}

In the next section we present our system design and show how it adheres
to these requirements.
